---
title: "Mtcars mile per gallone regression study"
author: "WangYong"
date: "2022/1/29"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- two pages

## 1. Executive Summary  
Based on both data explorary plot mode and linear model coefficients check, it can be confidence to answer below to questions:
## Q1. Is an automatic or manual transmission better for MPG?  
Yes. Compared to automatic transmission, manual is better for MPG. This answer will be showed in both boxplot EDA stage and linear mode coefficients interpret stage. 

### Q2. Quantify the MPG difference between automatic and manual transmissions
With stepAIC strategy to find the best model, we get quantified model :
   ** mpg =  9.6178 + 2.9358 * am  + (-3.9165)* wt + 1.2259 * qsec ** 
it means:
1. Model can explain for: 84.9663556% variability of mpg
2. Compared to reference mpg(9.6) automatic transmission type, every gallon fuel
could run extra 2.9358, that is 2.938+9.6178=12.558.
3. For every 1000lb weight added, the car will be run less -3.9165 miles.
4. the fast the miles will be added 1.2259 mileage per qsec.


## 2. Exploratory Data Analysis
The mtcars data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption(mpg) and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).   

### 2.1 quick look
First, let's quick look the data.
```{r head, echo=FALSE, message=FALSE,fig.width=5,cache=TRUE,warning=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
data(mtcars)
columns <-names(mtcars)
independent <-columns[!columns %in% ('mpg')]
response <-'mpg'

```
The mtcars dataset has `r dim(mtcars)[1]` rows. 
The response variable is 'mpg'. and the independent variables are 
`r independent[independent!=response]`

```{r echo=FALSE, message=FALSE,cache=TRUE}
mtcars <- mtcars %>% #mutate(transmission_type=as.character(am))  %>%
  mutate(tranmission_type=case_when( am==0~'automatic',am==1~'manual'))
#mtcars['transmission_type'] =
head(mtcars)
```
Then, let use box plot have a overview of mpg compare am transmission.

## 3. Q1. Is an automatic or manual transmission better for MPG?  
This question will be studied by boxplot and two sample t_test to compare.
# 3.1 Box plot  
```{r eda, echo=FALSE,messages=FALSE}
library(ggplot2)

g<-ggplot(data=mtcars, aes(fill=factor(tranmission_type),y=mpg))
g+geom_boxplot()+labs(
x='Transmission Type',
y= 'Miles(US)/gallon',
title = 'MPG boxplot in transmission_type')

```

For above figures, it can be clear find the different transmission type lead to different mile per gallon. The automatic transmission mean is about 17 miles per gallon. The manual type is a bit higher than automatic, 24 mile per gallon. 

### 3.2 two sample t test

```{r ttetst, echo=TRUE, message=FALSE}
library(dplyr)
mpg_auto   <- mtcars %>% filter(am==0) %>% select(mpg)
mpg_manual <- mtcars %>% filter(am==1) %>% select(mpg)

tt_result <-t.test(mpg_manual, mpg_auto, alternative='greater')

```
According to above two sample test, we **reject null hypothesis** with p_value **`r round(tt_result$p.value,4)*100`% **.    
It showed that the difference between manual and automatic transmission is significant and manual transmission car MPG is greater than the automatic type. 

After compared in by box plot, and student test, It can be confidences that that fuel consumption viewpoint, manual transmission type is better that automatic.

## 4.  Q2. Quantify the MPG difference between automatic and manual transmissions
In order to quantify the mpg difference between two different transmission type. we need look inside, 

### 4.1 Using stepAIC to final appropriate mode
There are 10 independent variable. They are: cyl, disp, hp, drat, wt, qsec, vs, am, gear, carb.
The stepAIC will be used to final appropriate model.
```{r stepAIC, echo=TRUE,  message=FALSE}

#aic_result<-  stepAIC(lm(data=mtcars, mpg~.),direction = 'both')
#aic_result$anova
final_model <- lm(data=mtcars, mpg~factor(am)+wt+qsec)
r2 <-summary(final_model)$r.squared
adj_r2<- summary(final_model)$adj.r.squared

residual_normality <-shapiro.test(final_model$residuals)
coef <-summary(final_model)$coef
summary(final_model)
```
With stepAIC strategy to find the best model, we get quantified model :
   ** mpg =  9.6178 + 2.9358 * am  + (-3.9165)* wt + 1.2259 * qsec ** 
it means:
1. Model can explain for: 84.9663556% variability of mpg
2. Compared to reference mpg(9.6) automatic transmission type, every gallon fuel
could run extra 2.9358, that is 2.938+9.6178=12.558.
3. For every 1000lb weight added, the car will be run less -3.9165 miles.
4. the fast the miles will be added 1.2259 mileage per qsec.


## 4.2 Vif & residual normality test
```{r vif, echo=FALSE, message=FALSE,warning=FALSE}
library(car)


residual_normality <- shapiro.test(final_model$residuals)$p.value
vif(final_model)
```
1. Multilinear: According to vif result, it showed possibility of multicollinear. If the VIF value less than 4, in general, there is no serious multicollinear issue.  
2. residual normality: According the shapiro normaility test, the p_value is `r residual_normality` which large that 0.05. So it can keep the null hypothesis, residual normality.


## 5. Appendix figures
### 5.1 residual vs fitted plot
```{r plot1, echo=FALSE}
plot(final_model,1)
```

### 5.2 Q-Q plot
```{r plot2, echo=FALSE}
plot(final_model,2)
```

### 5.3 scale-location
```{r plot3, echo=FALSE}
plot(final_model,3)
```

### 5.4 cook's distance
```{r plot4, echo=FALSE}
plot(final_model,4)
```
